Quantum Oracles - How to Transform Classical Problems into Quantum ones

### 2024-08-13 latex/paper.tex
updated paper

@@

\subsubsubsection{Aproximação de Milhas para Quilômetros usando Fibonacci}

Para aproximar o valor de milhas para quilômetros, podemos utilizar a sequência de Fibonacci com a seguinte relação: $F_{km} = F_{milhas}(n+1)$, sendo aqui $F$ a versão clássica de Fibonacci com $F(1) = 1$ e $F(2) = 2$. Dessa forma, se a posição $n$ é conhecida, valor aproximado em quilômetros será dado em $n+1$.

\begin{table}[!h]
	\begin{center}
		\begin{tabular}{ |c|c| } 
			\hline
			milhas & km \\
			\hline
			1 & 2 \\
			\hline
			2 & 3 \\
			\hline
			3 & 5 \\
			\hline
			5 & 8 \\
			\hline
		\end{tabular}
	\caption{valores aproximados de Milhas para Quilômetros}
	\end{center}
\end{table}

@@

Valores não presentes na sequência, podem ser aproximados repartindo o valor em partes menores. Por exemplo, para transformar $10$ milhas em quilômetros, podemos fazer: $8 + 2 = 10miles \to F(5) + F(2) \to F(5+1) + F(2+1) =  13 + 3 = 16km$, aproximando então do valor mais preciso de $\approx 16.0934$

\subsubsection{Implementação do circuito}
Com essa formulação, o algoritmo final segue esse fluxo:

\begin{algorithm}[H]
	\begin{algorithmic}
		\State{partes = $quebraValor(valorDeEntrada)$}
		\For{parte in partes}
			\State{Aplique o Oracle $F(parte)$}
			\State{Faça as medições nos qubits}
			\State{Reset os qubits usados}
		\EndFor
		\State{verifique o resultado de cada bit-string}
		\State{Multiplique cada resultado com o valor $i$ correspondente}

	\end{algorithmic}
	\caption{Algoritmo quântico para a conversão}
	\label{alg:miles-to-km-quantum-algortihm}
\end{algorithm}

>>>>

\captionsetup[table]{skip=5pt}

@@

\subsubsubsection{Approximating Miles to Kilometers}

To approximate the value from miles to kilometers, an old approach for that is using the Fibonacci sequence. This method, uses the relation $F_{km} = F_{milhas}(n+1)$, which $F$ is the classical Fibonacci algorithm ($F(1) = 1$ and $F(2) = 2$), and $n$ is a known position in this very sequence. Following this equation, the relative kilometers values will be given in the next \textit{n} ($n+1$).

\begin{table}[h]
	\begin{center}
		\begin{tabular}{ |c|c|c| } 
			\hline
			miles & Km & Real(Km) value\\
			\hline
			1 & 2 & 1.60934\\
			\hline
			2 & 3 & 3.21869\\
			\hline
			3 & 5 & 4.82803\\
			\hline
			5 & 8 & 8.04672\\
			\hline
		\end{tabular}
	\caption{Approximated miles-Km values}
	\end{center}
\end{table}

@@

For values that aren't present in the sequence, they can be generated combining multiple values which are there. For example, to transform $10$ miles to kilometers, we could use the values $8$ and $2$, which are known in the sequence, and then used the previous cited method for each part. So, for this example, $8 = F(5)$ and $2 = F(2)$, so $F(5 + 1) + F(2 + 1) = F(6) + F(3) = 13 + 3 = 16Km$ giving a close value of $\approx 16.0934Km$.

\subsubsection{Implementation}

Using the formulation above, the final algorithm takes place using a Hybrid approach, following the structure bellow:

\begin{algorithm}[h]
	\begin{algorithmic}
		\State{parts = $BreakInputIntoFibonacciParts(input)$}
		\For{parte in parts}
			\State{Apply the Oracle embedding $F(part)$}
			\State{Measure the Oracle Qubits}
			\State{Reset these Qubits}
		\EndFor
		\State{Check the outcomes}
		\State{Multiply the given result for its relative $i$}

	\end{algorithmic}
	\caption{Quantum Conversion algorithm}
	\label{alg:miles-to-km-quantum-algortihm}
\end{algorithm}
